---
title: "county_level_analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

You should be able to reproduce the analysis by running each code block below (in order). Pay attention to the ends of code blocks as they usually have lines to save files, but those lines are commented out (for safety reasons, since I never want to accidently override a saved file unless I'm sure I need to.)

# Data Processing
We need to determine which counties experienced exactly one significant damage event but also that the event did not happen to close to the beginning or end of their time series.

```{r}
library(data.table)
library(readr)
library(dplyr)
library(tidyverse)

df <- readRDS("../data/county_long.rds") |> filter(TAX_YEAR < 2020)
top <- quantile(df$TotPerCapADJ, probs = c(0.99)) # will look for county,year pairs where the county had per capita damage in the top 1 percentile

cols_to_keep <- c("TAX_YEAR", "geoid_2010", "TOT_REV", "TOT_EXP", "TOT_ASSET", "county_full", "state_name", "REGION", "DIVISION", "TotDmgADJ", "n_disasters", "TotPerCapADJ", "FEMA_threshADJ") # we don't need to keep every column to run the analysis

df <- df |> select(all_of(cols_to_keep))

df <- df |> mutate(topDamage = TotPerCapADJ >= top)
sum(df$topDamage) # 905 such instances

# counties are only eligible if at least one significant damage event occurred in their time series
eligible_counties <- df |> filter(topDamage) |> select(geoid_2010) |> unique() |> pull() # 657 eligible counties
df <- df |> filter(geoid_2010 %in% eligible_counties)

# Determine if significant damage events (i.e. being in top 1 percentile) occur in consecutive years 
df <- df |> group_by(geoid_2010) |> 
      arrange(TAX_YEAR, .by_group = TRUE) |>
      mutate(prev = lag(topDamage)) |>
      ungroup()

top_summary <- df |>
      group_by(geoid_2010) |>
      filter(topDamage) |>
      summarise(n_top = sum(topDamage),
                n_consecutive = sum(prev))

table(top_summary$n_top) # 492 counties with 1 change point, 113 with 2, 52 with 3 or more
table(top_summary$n_consecutive) # 615 with no consecutive, 37 with 1 or 2 consecutive
sum(is.na(df |> filter(topDamage) |> select(prev))) # 5; all due to being at beginning of time series
df |> filter(topDamage & is.na(prev) & TAX_YEAR != 1991) # 1 county whose time series began after 1991

# keep only the time series with one candidate change point
eligible_counties <- top_summary |> filter(n_top == 1) |> select(geoid_2010) |> pull() # 492
df <- df |> filter(geoid_2010 %in% eligible_counties)

gaps <- df |> group_by(geoid_2010) |>
      select(TAX_YEAR, geoid_2010, topDamage) |>
      mutate(min_year = min(TAX_YEAR),
             max_year = max(TAX_YEAR)) |>
      filter(topDamage) |>
      mutate(gap_before = TAX_YEAR-min_year, gap_after = max_year-TAX_YEAR)

# Keep only candidates that are not too close to the beginning or end of their time series
# TODO: to really catch the right buffer length I also should check that there actually exist 5 data points before and 4 after; currently we check the distance between the minimum and maximum year but if there is missing data in between then it would not be equivalent
eligible_counties <- gaps |> filter(gap_before >= 5 & gap_after >= 4) |> pull(geoid_2010) # 278 eligible

df <- df |> filter(geoid_2010 %in% eligible_counties)
df <- df |> mutate(TOT_REV = ifelse(TOT_REV < 0, 0, TOT_REV)) # there were 2 counties with negative total revenue; must address because we log the total revenue values for the analysis

if (!dir.exists("gp_data")) {dir.create("gp_data")}
# saveRDS(eligible_counties, "gp_data/top1counties.rds")
# saveRDS(df, "gp_data/top1countiesDF.rds")
```

# Hyperparameter Optimization
Before conducting the likelihood ratio tests, we find the values of the nu and nugget terms in the GP model for each eligible county that optimizes the likelihood. 

### Round 1: Grid Search w/ 50 counties
In this first round, we find the optimal parameters for 50 counties. We then apply k-means clustering to find the 5 centroids of nu,nugget pairs. These 5 coordinates become the initial starting points for gradient descent later on. 

```{r}
library(data.table)
library(readr)
library(dplyr)
library(tidyverse)
library(fields)
library(mvtnorm)

df <- readRDS("gp_data/top1countiesDF.rds")

get_likelihood_sigma <- function(row, dist_mat, rho, data){ # helper function for computing likelihood
      # Compute Matérn Covariance Matrix
      mat_cov <- Matern(d = dist_mat, smoothness = row[1], range = rho, phi = 1) + diag(row[2], dim(dist_mat)[1])
      
      # Compute sigma^2
      sigma.squared <- (1/length(data)) * (data %*% chol2inv(chol(mat_cov)) %*% data)[1,1] 
      
      # Compute likelihood
      likelihood <- dmvnorm(data, 
                            mean = rep(0, length(data)), 
                            sigma = sigma.squared * mat_cov,
                            log = TRUE)
      return(likelihood)
}

# distance matrix of years
dist_mat_all <- as.matrix(dist(sort(unique(df$TAX_YEAR) - min(df$TAX_YEAR) + 1), diag=TRUE, upper=TRUE))

set.seed(2727)
eligible_counties <- unique(df$geoid_2010)
eligible_counties <- sample(eligible_counties, size = 50)

combos <- expand.grid(nu = seq(from = 0.01, to = 3, by = 0.07475), 
                      nugget = seq(from = 0, to = 3, by = 0.1))

best_parameters.null <- setNames(data.frame(matrix(ncol = 3, nrow = 0)), c("ID", "nu", "nugget"))
best_parameters.L <- setNames(data.frame(matrix(ncol = 3, nrow = 0)), c("ID", "nu", "nugget"))
best_parameters.R <- setNames(data.frame(matrix(ncol = 3, nrow = 0)), c("ID", "nu", "nugget"))
for (countyID in eligible_counties) {
      # pull their time series
      my_data <- df |> filter(geoid_2010 == countyID) |>
            mutate(TOT_REV = log1p(TOT_REV),
                   TOT_EXP = log1p(TOT_EXP),
                   TOT_ASSET = log1p(TOT_ASSET))
      all_years <- my_data$TAX_YEAR - min(df$TAX_YEAR) + 1 # all the years we have data for this county
      log_rev <- my_data |> merge(data.frame(TAX_YEAR = 1991:2019), all = TRUE) |> arrange(TAX_YEAR) |> pull(TOT_REV)
      
      candidate <- (my_data  |> filter(topDamage) |> select(TAX_YEAR) |> pull()) - min(df$TAX_YEAR) + 1
      left_years <- all_years[1:which(all_years == candidate)-1]
      right_years <- all_years[which(all_years == candidate):length(all_years)]
      
      ### Null Model ###
      curr_all_years <- c(left_years, right_years)
      centered_rev <- log_rev[curr_all_years] - mean(log_rev[curr_all_years])
      dist_mat <- dist_mat_all[curr_all_years, curr_all_years]
      dist_mat <- (dist_mat - min(dist_mat)) / (max(dist_mat) - min(dist_mat))
      
      likelihood_wrapper.null <- function(pars.vec){
            return(get_likelihood_sigma(row = pars.vec,
                                             dist_mat = dist_mat,
                                             rho = 1,
                                             data = centered_rev))
      }
      
      likelihoods.null <- apply(combos, MARGIN = 1, likelihood_wrapper.null)
      tst <- as.data.frame(list(nu = combos$nu, nugget = combos$nugget, likelihood = likelihoods.null))
      best_parameters.null <- rbind(best_parameters.null, 
                                    as.data.frame(list(geoid = countyID,
                                                       nu = tst[which.max(tst$likelihood),]$nu,
                                                       nugget = tst[which.max(tst$likelihood),]$nugget)))
      
      ### Alternative Model ###
      
      # Left
      centered_rev.L <- log_rev[left_years] - mean(log_rev[left_years])
      dist_mat.L <- dist_mat_all[left_years, left_years]
      dist_mat.L <- (dist_mat.L - min(dist_mat.L)) / (max(dist_mat.L) - min(dist_mat.L))
      
      likelihood_wrapper.left <- function(pars.vec){
            return(get_likelihood_sigma(row = pars.vec,
                                             dist_mat = dist_mat.L,
                                             rho = 1,
                                             data = centered_rev.L))
      }
      
      likelihoods.L <- apply(combos, MARGIN = 1, likelihood_wrapper.left)
      tst <- as.data.frame(list(nu = combos$nu, nugget = combos$nugget, likelihood = likelihoods.L))
      best_parameters.L <- rbind(best_parameters.L, 
                                    as.data.frame(list(geoid = countyID,
                                                       nu = tst[which.max(tst$likelihood),]$nu,
                                                       nugget = tst[which.max(tst$likelihood),]$nugget)))
      
      # Right
      centered_rev.R <- log_rev[right_years] - mean(log_rev[right_years])
      dist_mat.R <- dist_mat_all[right_years, right_years]
      dist_mat.R <- (dist_mat.R - min(dist_mat.R)) / (max(dist_mat.R) - min(dist_mat.R))
      
      likelihood_wrapper.right <- function(pars.vec){
            return(get_likelihood_sigma(row = pars.vec,
                                             dist_mat = dist_mat.R,
                                             rho = 1,
                                             data = centered_rev.R))
      }
      
      likelihoods.R <- apply(combos, MARGIN = 1, likelihood_wrapper.right)
      tst <- as.data.frame(list(nu = combos$nu, nugget = combos$nugget, likelihood = likelihoods.R))
      best_parameters.R <- rbind(best_parameters.R, 
                                    as.data.frame(list(geoid = countyID,
                                                       nu = tst[which.max(tst$likelihood),]$nu,
                                                       nugget = tst[which.max(tst$likelihood),]$nugget)))
}

all_best <- rbind(best_parameters.null, best_parameters.L, best_parameters.R) |> select(nu,nugget)
cl <- kmeans(all_best, 5, iter.max = 20, nstart = 3)

# saveRDS(cl, "gp_data/init_conds_50.rds")
```

### Round 2: Gradient Descent (Nelder-Mead) with multiple starts for all counties
```{r}
library(data.table)
library(readr)
library(dplyr)
library(tidyverse)
library(fields)
library(mvtnorm)

df <- readRDS("gp_data/top1countiesDF.rds")

get_likelihood_sigma <- function(row, dist_mat, rho, data){ # helper function for computing likelihood
      # Compute Matérn Covariance Matrix
      mat_cov <- Matern(d = dist_mat, smoothness = row[1], range = rho, phi = 1) + diag(row[2], dim(dist_mat)[1])
      
      # Compute sigma^2
      sigma.squared <- (1/length(data)) * (data %*% chol2inv(chol(mat_cov)) %*% data)[1,1] 
      
      # Compute likelihood
      likelihood <- dmvnorm(data, 
                            mean = rep(0, length(data)), 
                            sigma = sigma.squared * mat_cov,
                            log = TRUE)
      return(likelihood)
}

# distance matrix of years
dist_mat_all <- as.matrix(dist(sort(unique(df$TAX_YEAR) - min(df$TAX_YEAR) + 1), diag=TRUE, upper=TRUE))

init_conds <- readRDS("gp_data/init_conds_50.rds")$centers

best_parameters.null <- setNames(data.frame(matrix(ncol = 3, nrow = 0)), c("ID", "nu", "nugget"))
best_parameters.L <- setNames(data.frame(matrix(ncol = 3, nrow = 0)), c("ID", "nu", "nugget"))
best_parameters.R <- setNames(data.frame(matrix(ncol = 3, nrow = 0)), c("ID", "nu", "nugget"))

errs <- c()
for (countyID in unique(df$geoid_2010)) {
      print(countyID)
      # pull their time series
      my_data <- df |> filter(geoid_2010 == countyID) |>
            mutate(TOT_REV = log1p(TOT_REV),
                   TOT_EXP = log1p(TOT_EXP),
                   TOT_ASSET = log1p(TOT_ASSET))
      all_years <- my_data$TAX_YEAR - min(df$TAX_YEAR) + 1 # all the years we have data for this county
      log_rev <- my_data |> merge(data.frame(TAX_YEAR = 1991:2019), all = TRUE) |> arrange(TAX_YEAR) |> pull(TOT_REV)
      
      candidate <- (my_data  |> filter(topDamage) |> select(TAX_YEAR) |> pull()) - min(df$TAX_YEAR) + 1
      left_years <- all_years[1:which(all_years == candidate)-1]
      right_years <- all_years[which(all_years == candidate):length(all_years)]
      
      ### Null Model ###
      curr_all_years <- c(left_years, right_years)
      centered_rev <- log_rev[curr_all_years] - mean(log_rev[curr_all_years])
      dist_mat <- dist_mat_all[curr_all_years, curr_all_years]
      dist_mat <- (dist_mat - min(dist_mat)) / (max(dist_mat) - min(dist_mat))
      
      likelihood_wrapper.null <- function(pars.vec){
            return(-1 * get_likelihood_sigma(row = pars.vec,
                                             dist_mat = dist_mat,
                                             rho = 1,
                                             data = centered_rev))
      }
      
      tst <- setNames(data.frame(matrix(ncol = 6, nrow = 0)), c("nu.init", "nugg.init", "nu", "nugget", "likelihood", "trial"))
i <- 2      
      for (i in 1:nrow(init_conds)){
            res <- constrOptim(theta = init_conds[i,], 
                               f = likelihood_wrapper.null,
                               grad = NULL,
                               ui = rbind(c(1,0),c(-1,0),c(0,1)), #rbind(c(1,0),c(-1,0),c(0,1))
                               ci = c(0.001,-3.5,0)) #c(0.001,-3.5, 0)
            tst[nrow(tst)+1,] <- c(c(init_conds[i,1], init_conds[i,2], res$par[1], res$par[2], -1*res$value, i))
      }

      best_parameters.null <- rbind(best_parameters.null, 
                                    as.data.frame(list(geoid = countyID,
                                                       nu = tst[which.max(tst$likelihood),]$nu,
                                                       nugget = tst[which.max(tst$likelihood),]$nugget)))
      
      ### Alternative Model ###
      
      # Left
      centered_rev.L <- log_rev[left_years] - mean(log_rev[left_years])
      if (var(centered_rev.L) == 0){
            errs <- c(errs, countyID)
            next
            }
      dist_mat.L <- dist_mat_all[left_years, left_years]
      dist_mat.L <- (dist_mat.L - min(dist_mat.L)) / (max(dist_mat.L) - min(dist_mat.L))
      
      likelihood_wrapper.left <- function(pars.vec){
            return(-1 * get_likelihood_sigma(row = pars.vec,
                                             dist_mat = dist_mat.L,
                                             rho = 1,
                                             data = centered_rev.L))
      }
      
      tst <- setNames(data.frame(matrix(ncol = 6, nrow = 0)), c("nu.init", "nugg.init", "nu", "nugget", "likelihood", "trial"))
      for (i in 1:nrow(init_conds)){
            res <- constrOptim(theta = init_conds[i,], 
                               f = likelihood_wrapper.left,
                               grad = NULL,
                               ui = rbind(c(1,0),c(-1,0),c(0,1)), #rbind(c(1,0),c(-1,0),c(0,1))
                               ci = c(0.001,-3.5,0)) #c(0.001,-3.5, 0)
            tst[nrow(tst)+1,] <- c(c(init_conds[i,1], init_conds[i,2], res$par[1], res$par[2], -1*res$value, i))
      }
      best_parameters.L <- rbind(best_parameters.L, 
                                    as.data.frame(list(geoid = countyID,
                                                       nu = tst[which.max(tst$likelihood),]$nu,
                                                       nugget = tst[which.max(tst$likelihood),]$nugget)))
      
      # Right
      centered_rev.R <- log_rev[right_years] - mean(log_rev[right_years])
      if (var(centered_rev.R) == 0){
            errs <- c(errs, countyID)
            next
            }
      dist_mat.R <- dist_mat_all[right_years, right_years]
      dist_mat.R <- (dist_mat.R - min(dist_mat.R)) / (max(dist_mat.R) - min(dist_mat.R))
      
      likelihood_wrapper.right <- function(pars.vec){
            return(-1 * get_likelihood_sigma(row = pars.vec,
                                             dist_mat = dist_mat.R,
                                             rho = 1,
                                             data = centered_rev.R))
      }
      
      tst <- setNames(data.frame(matrix(ncol = 6, nrow = 0)), c("nu.init", "nugg.init", "nu", "nugget", "likelihood", "trial"))
      for (i in 1:nrow(init_conds)){
            res <- constrOptim(theta = init_conds[i,], 
                               f = likelihood_wrapper.right,
                               grad = NULL,
                               ui = rbind(c(1,0),c(-1,0),c(0,1)), #rbind(c(1,0),c(-1,0),c(0,1))
                               ci = c(0.001,-3.5,0)) #c(0.001,-3.5, 0)
            tst[nrow(tst)+1,] <- c(c(init_conds[i,1], init_conds[i,2], res$par[1], res$par[2], -1*res$value, i))
      }
      best_parameters.R <- rbind(best_parameters.R, 
                                    as.data.frame(list(geoid = countyID,
                                                       nu = tst[which.max(tst$likelihood),]$nu,
                                                       nugget = tst[which.max(tst$likelihood),]$nugget)))

}

# saveRDS(best_parameters.null, "gp_data/best_null.rds")
# saveRDS(best_parameters.L, "gp_data/best_L.rds")
# saveRDS(best_parameters.R, "gp_data/best_R.rds")
```


# Likelihood Ratio Test
```{r}
library(data.table)
library(readr)
library(dplyr)
library(tidyverse)
library(fields)
library(mvtnorm)

df <- readRDS("gp_data/top1countiesDF.rds")

# distance matrix of years
dist_mat_all <- as.matrix(dist(sort(unique(df$TAX_YEAR) - min(df$TAX_YEAR) + 1), diag=TRUE, upper=TRUE))

best_all.null <- readRDS("gp_data/best_null.rds")
best_all.L <- readRDS("gp_data/best_L.rds")
best_all.R <- readRDS("gp_data/best_R.rds")
rho = 1

reject_null <- list()
for (my_county in unique(df$geoid_2010)) {
      if (my_county == "21223"){ # this was one case where left was all 0s
            next
      }
      # pull their time series
      my_data <- df |> filter(geoid_2010 == my_county) |>
            mutate(TOT_REV = log1p(TOT_REV),
                   TOT_EXP = log1p(TOT_EXP),
                   TOT_ASSET = log1p(TOT_ASSET))
      all_years <- my_data$TAX_YEAR - min(df$TAX_YEAR) + 1 # all the years we have data for this county
      log_rev <- my_data |> merge(data.frame(TAX_YEAR = 1991:2019), all = TRUE) |> arrange(TAX_YEAR) |> pull(TOT_REV)
      
      candidate <- (my_data  |> filter(topDamage) |> select(TAX_YEAR) |> pull()) - min(df$TAX_YEAR) + 1
      
      # pull best parameters
      best.null <- best_all.null |> filter(geoid == my_county)
      best.L <- best_all.L |> filter(geoid == my_county)
      best.R <- best_all.R |> filter(geoid == my_county)
      

      # Determine the left and right time series corresponding to the current candidate change point
      left_years <- all_years[1:which(all_years == candidate)-1]
      right_years <- all_years[which(all_years == candidate):length(all_years)]
      
      ### Null Hypothesis Model ###
      curr_all_years <- c(left_years, right_years) # Redundant for single candidate
      centered_rev <- log_rev[curr_all_years] - mean(log_rev[curr_all_years]) # center the log revenue values so they are mean 0
      
      dist_mat <- dist_mat_all[curr_all_years, curr_all_years]
      dist_mat <- (dist_mat - min(dist_mat)) / (max(dist_mat) - min(dist_mat))
      Sigma_0 <- Matern(d = dist_mat,
                        smoothness = best.null$nu,
                        range = rho,
                        phi = 1) + diag(best.null$nugget, dim(dist_mat)[1])
      
      sigma.sqrd_0 <- (1/length(centered_rev)) * (centered_rev %*% chol2inv(chol(Sigma_0)) %*% centered_rev)[1,1]
      Sigma_0 <- sigma.sqrd_0 * Sigma_0
      
      ### Alternative Hypothesis Model ###
      # center the log revenue values so they are mean 0
      centered_rev.L <- log_rev[left_years] - mean(log_rev[left_years])
      centered_rev.R <- log_rev[right_years] - mean(log_rev[right_years])
      
      # compute and normalize distance matrices
      dist_mat.L <- dist_mat_all[left_years, left_years]
      dist_mat.L <- (dist_mat.L - min(dist_mat.L)) / (max(dist_mat.L) - min(dist_mat.L))
      
      dist_mat.R <- dist_mat_all[right_years, right_years]
      dist_mat.R <- (dist_mat.R - min(dist_mat.R)) / (max(dist_mat.R) - min(dist_mat.R))
      
      # Compute Matern covariance matrices
      Sigma_L <- Matern(d = dist_mat.L,
                  smoothness = best.L$nu,
                  range = rho,
                  phi = 1) + diag(best.L$nugget, dim(dist_mat.L)[1])
      sigma.sqrd_L <- (1/length(left_years)) * (centered_rev.L %*% chol2inv(chol(Sigma_L)) %*% centered_rev.L)[1,1]
      Sigma_L <- sigma.sqrd_L * Sigma_L
      
      Sigma_R <- Matern(d = dist_mat.R,
                  smoothness = best.R$nu,
                  range = rho,
                  phi = 1) + diag(best.R$nugget, dim(dist_mat.R)[1])
      sigma.sqrd_R <- (1/length(right_years)) * (centered_rev.R %*% chol2inv(chol(Sigma_R)) %*% centered_rev.R)[1,1]
      Sigma_R <- sigma.sqrd_R * Sigma_R
      
      ### Likelihood Ratio Test ###
      L_0 <- dmvnorm(centered_rev, 
                     mean = rep(0, length(centered_rev)), 
                     sigma = Sigma_0,
                     log = TRUE)
      
      L_left <- dmvnorm(centered_rev.L, 
                        mean = rep(0, length(centered_rev.L)), 
                        sigma = Sigma_L,
                        log = TRUE)
      
      L_right <- dmvnorm(centered_rev.R, 
                         mean = rep(0, length(centered_rev.R)), 
                         sigma = Sigma_R,
                         log = TRUE)
      
      L_alt <- L_left + L_right

      
      # likelihood ratio test statistic
      lrt <- -2*L_0 + 2*L_alt
      doF <- 4 #  (mu1, mu2, Sigma1, Sigma2, nu1, nu2, nugget1, nugget2) vs (mu, Sigma, nu, nugget) 
      reject_null[my_county] <- (lrt > qchisq(p = 0.05, df = doF, lower.tail = FALSE))
}
# rm(list = setdiff(ls(), c("df", "eligible_counties", "gaps", "top_summary")))
sum(unlist(reject_null)) / length(reject_null) # 57.8% of the time we have enough evidence to reject the null
```


# Empirical Distribution County-Level

```{r}
library(readr)
library(dplyr)
library(tidyverse)

set.seed(2727)
df <- readRDS("gp_data/top1countiesDF.rds")
eligible_counties <- unique(df$geoid_2010)

# We are going to pick random candidate points within each county's time series, but still need to ensure that its not too close to the beginning or end
df <- df |> filter(geoid_2010 != "21223") |> 
      group_by(geoid_2010) |>
      mutate(n = n(),
             row_num = row_number(),
             eligible = (row_num > 5 & row_num <= n-4)) |> ungroup()

candidates_all <- list()
for (i in 1:50) {
      candidates <- df |> group_by(geoid_2010) |>
            filter(eligible) |>
            slice_sample(n = 1) |>
            select(geoid_2010, TAX_YEAR)
      
      candidates_list <- candidates |> pull(TAX_YEAR) |> as.list()
      names(candidates_list) <- candidates |> pull(geoid_2010)
      
      candidates_all[[as.character(i)]] <- candidates_list
}

# saveRDS(candidates_all, "gp_data/random_candidates50.rds")
```

## Hyperparameter Opt
### Round One: Grid Search w/ 50 counties
```{r}
library(data.table)
library(readr)
library(dplyr)
library(tidyverse)
library(fields)
library(mvtnorm)

candidates_all <- readRDS("gp_data/random_candidates50.rds")
df <- readRDS("gp_data/top1countiesDF.rds")

get_likelihood_sigma <- function(row, dist_mat, rho, data){ # helper function for computing likelihood
      # Compute Matérn Covariance Matrix
      mat_cov <- Matern(d = dist_mat, smoothness = row[1], range = rho, phi = 1) + diag(row[2], dim(dist_mat)[1])
      
      # Compute sigma^2
      sigma.squared <- (1/length(data)) * (data %*% chol2inv(chol(mat_cov)) %*% data)[1,1] 
      
      # Compute likelihood
      likelihood <- dmvnorm(data, 
                            mean = rep(0, length(data)), 
                            sigma = sigma.squared * mat_cov,
                            log = TRUE)
      return(likelihood)
}

# distance matrix of years
dist_mat_all <- as.matrix(dist(sort(unique(df$TAX_YEAR) - min(df$TAX_YEAR) + 1), diag=TRUE, upper=TRUE))

set.seed(2727)
eligible_counties <- sample(unique(df$geoid_2010), size = 50)

combos <- expand.grid(nu = seq(from = 0.01, to = 3, by = 0.07475), 
                      nugget = seq(from = 0, to = 3, by = 0.1))

best_parameters.null <- setNames(data.frame(matrix(ncol = 4, nrow = 0)), c("ID", "nu", "nugget", "trial"))
best_parameters.L <- setNames(data.frame(matrix(ncol = 4, nrow = 0)), c("ID", "nu", "nugget", "trial"))
best_parameters.R <- setNames(data.frame(matrix(ncol = 4, nrow = 0)), c("ID", "nu", "nugget", "trial"))

for (countyID in eligible_counties) {
      print(countyID)
      # pull their time series
      my_data <- df |> filter(geoid_2010 == countyID) |>
            mutate(TOT_REV = log1p(TOT_REV),
                   TOT_EXP = log1p(TOT_EXP),
                   TOT_ASSET = log1p(TOT_ASSET))
      all_years <- my_data$TAX_YEAR - min(df$TAX_YEAR) + 1 # all the years we have data for this county
      log_rev <- my_data |> merge(data.frame(TAX_YEAR = 1991:2019), all = TRUE) |> arrange(TAX_YEAR) |> pull(TOT_REV)
      
      for (i in names(candidates_all)){
            candidate <- candidates_all[[i]][[countyID]] - min(df$TAX_YEAR) + 1
            left_years <- all_years[1:which(all_years == candidate)-1]
            right_years <- all_years[which(all_years == candidate):length(all_years)]
            
            ### Null Model ###
            curr_all_years <- c(left_years, right_years)
            centered_rev <- log_rev[curr_all_years] - mean(log_rev[curr_all_years])
            dist_mat <- dist_mat_all[curr_all_years, curr_all_years]
            dist_mat <- (dist_mat - min(dist_mat)) / (max(dist_mat) - min(dist_mat))
            
            # grid search (if doing Nelder-Mead, multiply get_likelihood_sigma by -1)
            likelihood_wrapper.null <- function(pars.vec){
                  return(get_likelihood_sigma(row = pars.vec,
                                                   dist_mat = dist_mat,
                                                   rho = 1,
                                                   data = centered_rev))
            }
            
            likelihoods.null <- apply(combos, MARGIN = 1, likelihood_wrapper.null)
            tst <- as.data.frame(list(nu = combos$nu, nugget = combos$nugget, likelihood = likelihoods.null))
            best_parameters.null <- rbind(best_parameters.null, 
                                          as.data.frame(list(geoid = countyID,
                                                             nu = tst[which.max(tst$likelihood),]$nu,
                                                             nugget = tst[which.max(tst$likelihood),]$nugget,
                                                             trial = i)))
            
            ### Alternative Model ###
            
            # Left
            centered_rev.L <- log_rev[left_years] - mean(log_rev[left_years])
            dist_mat.L <- dist_mat_all[left_years, left_years]
            dist_mat.L <- (dist_mat.L - min(dist_mat.L)) / (max(dist_mat.L) - min(dist_mat.L))
            
            likelihood_wrapper.left <- function(pars.vec){
                  return(get_likelihood_sigma(row = pars.vec,
                                                   dist_mat = dist_mat.L,
                                                   rho = 1,
                                                   data = centered_rev.L))
            }
            
            likelihoods.L <- apply(combos, MARGIN = 1, likelihood_wrapper.left)
            tst <- as.data.frame(list(nu = combos$nu, nugget = combos$nugget, likelihood = likelihoods.L))
            best_parameters.L <- rbind(best_parameters.L, 
                                          as.data.frame(list(geoid = countyID,
                                                             nu = tst[which.max(tst$likelihood),]$nu,
                                                             nugget = tst[which.max(tst$likelihood),]$nugget,
                                                             trial = i)))
            
            # Right
            centered_rev.R <- log_rev[right_years] - mean(log_rev[right_years])
            dist_mat.R <- dist_mat_all[right_years, right_years]
            dist_mat.R <- (dist_mat.R - min(dist_mat.R)) / (max(dist_mat.R) - min(dist_mat.R))
            
            likelihood_wrapper.right <- function(pars.vec){
                  return(get_likelihood_sigma(row = pars.vec,
                                                   dist_mat = dist_mat.R,
                                                   rho = 1,
                                                   data = centered_rev.R))
            }
            
            likelihoods.R <- apply(combos, MARGIN = 1, likelihood_wrapper.right)
            tst <- as.data.frame(list(nu = combos$nu, nugget = combos$nugget, likelihood = likelihoods.R))
            best_parameters.R <- rbind(best_parameters.R, 
                                          as.data.frame(list(geoid = countyID,
                                                             nu = tst[which.max(tst$likelihood),]$nu,
                                                             nugget = tst[which.max(tst$likelihood),]$nugget,
                                                             trial = i)))
      }
}

all_best <- rbind(best_parameters.null, best_parameters.L, best_parameters.R) |> select(nu,nugget)
cl <- kmeans(all_best, 5, iter.max = 20, nstart = 3)
# saveRDS(cl, "gp_data/empirical_init_conds_50.rds")
# cl$centers
```

### Round Two: Gradient Descent (Nelder-Mead) with multiple starts for all counties
This part is in a separate R file called "empirical_opt.R" due to wanting the ability to run in parallel in the background. Before proceeding to the next section, run empirical_opt.R.

## LRT
First, glue together the two halves of data generated by empirical_opt.R.
```{r}
library(readr)
library(dplyr)
library(tidyverse)

glued <- rbind(readRDS( "gp_data/best_empirical_1stHalf.rds"), 
               readRDS( "gp_data/best_empirical_2ndHalf.rds"))

best_all <- glued |> 
      mutate(ID = paste0(geoid,".",trial)) |> 
      select(-geoid,-trial)
best_all <- split(best_all, best_all$ID)
best_all <- lapply(best_all, function(x) {split(x,x$type)})

saveRDS(best_all, "gp_data/best_empirical_all.rds")
```

Then, we run a likelihood ratio test for each county for each randomly selected candidate to get a list of true/false values per county (where true means "reject the null").
```{r}
library(readr)
library(dplyr)
library(tidyverse)
library(fields)
library(mvtnorm)

candidates_all <- readRDS("gp_data/random_candidates50.rds")
df <- readRDS("gp_data/top1countiesDF.rds")

# distance matrix of years
dist_mat_all <- as.matrix(dist(sort(unique(df$TAX_YEAR) - min(df$TAX_YEAR) + 1), diag=TRUE, upper=TRUE))

best_all <- readRDS("gp_data/best_empirical_all.rds")

rho = 1

reject_null_all <- setNames(vector("list", length(candidates_all)), names(candidates_all))
for (trialID in 1:length(candidates_all)) {
      reject_null <- list()
      for (countyID in unique(df$geoid_2010)){
            ID <- paste0(countyID, ".", trialID)
            print(ID)
            # pull their time series
            my_data <- df |> filter(geoid_2010 == countyID) |>
                  mutate(TOT_REV = log1p(TOT_REV))
            all_years <- my_data$TAX_YEAR - min(df$TAX_YEAR) + 1 # all the years we have data for this county
            log_rev <- my_data |> merge(data.frame(TAX_YEAR = 1991:2019), all = TRUE) |> arrange(TAX_YEAR) |> pull(TOT_REV)
            
            candidate <- candidates_all[[trialID]][[countyID]] - min(df$TAX_YEAR) + 1
            
            if (length(candidate)==0){ next }
            
            # pull best parameters
            best.curr <- best_all[[ID]] # best.curr$left$nu
      
            # Determine the left and right time series corresponding to the current candidate change point
            left_years <- all_years[1:which(all_years == candidate)-1]
            right_years <- all_years[which(all_years == candidate):length(all_years)]
            
            ### Null Hypothesis Model ###
            curr_all_years <- c(left_years, right_years) # Redundant for single candidate
            centered_rev <- log_rev[curr_all_years] - mean(log_rev[curr_all_years]) # center the log revenue values so they are mean 0
            
            dist_mat <- dist_mat_all[curr_all_years, curr_all_years]
            dist_mat <- (dist_mat - min(dist_mat)) / (max(dist_mat) - min(dist_mat))
            Sigma_0 <- Matern(d = dist_mat,
                              smoothness = best.curr$null$nu,
                              range = rho,
                              phi = 1) + diag(best.curr$null$nugget, dim(dist_mat)[1])
            
            sigma.sqrd_0 <- (1/length(centered_rev)) * (centered_rev %*% chol2inv(chol(Sigma_0)) %*% centered_rev)[1,1]
            Sigma_0 <- sigma.sqrd_0 * Sigma_0
            
            ### Alternative Hypothesis Model ###
            # center the log revenue values so they are mean 0
            centered_rev.L <- log_rev[left_years] - mean(log_rev[left_years])
            centered_rev.R <- log_rev[right_years] - mean(log_rev[right_years])
            
            # compute and normalize distance matrices
            dist_mat.L <- dist_mat_all[left_years, left_years]
            dist_mat.L <- (dist_mat.L - min(dist_mat.L)) / (max(dist_mat.L) - min(dist_mat.L))
            
            dist_mat.R <- dist_mat_all[right_years, right_years]
            dist_mat.R <- (dist_mat.R - min(dist_mat.R)) / (max(dist_mat.R) - min(dist_mat.R))
            
            # Compute Matern covariance matrices
            Sigma_L <- Matern(d = dist_mat.L,
                        smoothness = best.curr$left$nu,
                        range = rho,
                        phi = 1) + diag(best.curr$left$nugget, dim(dist_mat.L)[1])
            sigma.sqrd_L <- (1/length(left_years)) * (centered_rev.L %*% chol2inv(chol(Sigma_L)) %*% centered_rev.L)[1,1]
            Sigma_L <- sigma.sqrd_L * Sigma_L
            
            Sigma_R <- Matern(d = dist_mat.R,
                        smoothness = best.curr$right$nu,
                        range = rho,
                        phi = 1) + diag(best.curr$right$nugget, dim(dist_mat.R)[1])
            sigma.sqrd_R <- (1/length(right_years)) * (centered_rev.R %*% chol2inv(chol(Sigma_R)) %*% centered_rev.R)[1,1]
            Sigma_R <- sigma.sqrd_R * Sigma_R
            
            ### Likelihood Ratio Test ###
            L_0 <- dmvnorm(centered_rev, 
                           mean = rep(0, length(centered_rev)), 
                           sigma = Sigma_0,
                           log = TRUE)
            
            L_left <- dmvnorm(centered_rev.L, 
                              mean = rep(0, length(centered_rev.L)), 
                              sigma = Sigma_L,
                              log = TRUE)
            
            L_right <- dmvnorm(centered_rev.R, 
                               mean = rep(0, length(centered_rev.R)), 
                               sigma = Sigma_R,
                               log = TRUE)
            
            L_alt <- L_left + L_right
      
            
            # likelihood ratio test statistic
            lrt <- -2*L_0 + 2*L_alt
            doF <- 4 #  (mu1, mu2, Sigma1, Sigma2, nu1, nu2, nugget1, nugget2) vs (mu, Sigma, nu, nugget)
            reject_null[[countyID]] <- (lrt > qchisq(p = 0.05, df = doF, lower.tail = FALSE))

      }
      reject_null_all[[as.character(trialID)]] <- reject_null
}

# res <- unlist(lapply(reject_null_all, function(x){sum(unlist(x)) / length(x)}))
# hist(res)
# sd(res)
```

Finally, we will bootstrap for each county to get a large list of proportions of true to false.
```{r}
library(doParallel)

res <- unlist(unname(reject_null_all))
res <- split(res, names(res))
res <- lapply (res, unname)

empirical <- foreach(i = 1:1000, .inorder = FALSE) %do% {
      tst <- lapply(res, function(x){sample(x, 1)})
      sum(unlist(tst)) / length(tst)
}

hist(unlist(empirical), col = "#1796D2", 
     main = "County-Level Empirical Distribution", 
     xlab = "Proportion of times the null is rejected")
q <- quantile(unlist(empirical), probs = c(0.025, 0.5, 0.975)) # middle 95% of data is between 50.9% and 58.8%
q

# Since our county-level analysis (non-empirical) rejected the null 57% of the time, but 57% falls within the range [50.9%, 58.8%], we conclude the result is not significant.
```


