---
title: "org_level_analysis"
output: html_document
---

You should be able to reproduce the analysis by running each code block below (in order). Pay attention to the ends of code blocks as they usually have lines to save files, but those lines are usually commented out (for safety reasons, since I never want to accidentally override a saved file unless I'm sure I need to.)

# Data Processing
First some pre-processing to determine which organizations from the same eligible counties in the county analysis are themselves eligible. The reason that not all will be is that some organizations will have a shorter time series, so its possible that the disaster year for the county its in is too close to the beginning or end of the organization.

```{r}
library(data.table)
library(readr)
library(dplyr)
library(tidyverse)
library(fields)
library(mvtnorm)

eligible_counties <- readRDS("gp_data/top1counties.rds")
df <- readRDS("gp_data/top1countiesDF.rds")

# list of the candidate change points
df.changes <- df |> filter(topDamage) |> select(geoid_2010,TAX_YEAR)
# tst <- as.list(df.changes$TAX_YEAR)
# names(tst) <- df.changes$geoid_2010

df <- readRDS("../data/mega.rds") |> filter(TAX_YEAR <= 2019) # 13,211,506 records; 1,235,390 organizations

# Adjust dollar amounts for inflation to the year 2019
adj2019 <- as.data.frame(read_csv("../data/usd_2019_conv.csv", show_col_types = FALSE))
df <- merge(df, adj2019, by.x = "TAX_YEAR", by.y = "YEAR")
df <- df |> mutate(TOT_ASSET_OG = TOT_ASSET,
                   TOT_REV_OG = TOT_REV,
                   TOT_EXP_OG = TOT_EXP,
                   TOT_ASSET = TOT_ASSET * ADJ_2019,
                   TOT_REV = TOT_REV * ADJ_2019,
                   TOT_EXP = TOT_EXP * ADJ_2019)
# Optional, just to keep minimal number of columns
df <- df |> select(-TOT_ASSET_OG, -TOT_REV_OG, -TOT_EXP_OG, -DATA_COUNT)

# July 14, 2026: if negative, convert to 0 since we have to log values later
df <- df |> mutate(TOT_REV = ifelse(TOT_REV < 0, 0, TOT_REV),
                   TOT_ASSET = ifelse(TOT_ASSET < 0, 0, TOT_ASSET),
                   TOT_EXP = ifelse(TOT_EXP < 0, 0, TOT_EXP))

# IDs for two counties were changed after 2010. Some datasets use latest ID, others use 2010 ID
df <- df |> mutate(geoid_2010 = county.census.geoid)
df$geoid_2010[df$county.census.geoid == "02158"] <- "02270"
df$geoid_2010[df$county.census.geoid == "46102"] <- "46113"

# Now we need to figure out which orgs we actually will be able to use
# For sure if they have less than 10 records they won't be eligible
df <- df |> filter(geoid_2010 %in% eligible_counties) |> filter(!is.na(TOT_REV)) # 496,587 records from 48,300 orgs
df <- df |> group_by(EIN2) |> 
      mutate(DATA_COUNT = n()) |> 
      ungroup() |> filter(DATA_COUNT >= 10) # 401,352 records from 21,296 orgs

# Now need to make sure there is an appropriate number of records before and after the suspected change point
# First, let's make sure that we are only looking at orgs that have an existing record during the candidate change point year
df <- merge(df, df.changes |> mutate(topDamage = TRUE), 
            all.x = TRUE, by = c("geoid_2010", "TAX_YEAR"))
df <- df |> mutate(topDamage = replace_na(topDamage, FALSE))

eligible_orgs <- df |> group_by(EIN2) |> 
      summarize(eligible = (sum(topDamage)) > 0) |> 
      filter(eligible) |>
      pull(EIN2) # 15,573 orgs 

df <- df |> filter(EIN2 %in% eligible_orgs) # 316,854 records from 15,573 orgs 

# side quest resolving duplicates.. just removing all records in question for now
bad_groups <- df |> group_by(EIN2, TAX_YEAR) |>
      summarize(n = n(), .groups = "keep") |>
      filter(n > 1) # 562 org,year pairs that are unresolved dupes
bad_groups <- bad_groups |>  select(-n) |> mutate(keep = FALSE)

df <- merge(df, bad_groups, all.x = TRUE, by = c("EIN2", "TAX_YEAR")) |>
      mutate(keep = replace_na(keep, TRUE)) |>
      filter(keep) # 315,729 records from 15,573 orgs 

# Now, let's make sure there is an appropriate buffer around the change point
gaps <- df |> 
      group_by(EIN2) |>
      arrange(TAX_YEAR) |>
      summarise(before = sum(row_number() < which(topDamage)),
             after = sum(row_number() > which(topDamage)))

eligible_orgs <- gaps |> filter(before >= 5 & after >= 4) |> pull(EIN2) # 11,164 orgs

# saveRDS(df |> filter(EIN2 %in% eligible_orgs), "gp_data/df_eligible_orgs.rds") # 246,231 records
```

# Hyperparameter Optimization
## Round 1: Grid Search on 50 orgs
```{r}
library(data.table)
library(readr)
library(dplyr)
library(tidyverse)
library(fields)
library(mvtnorm)

df <- readRDS("gp_data/df_eligible_orgs.rds") |> select(-DATA_COUNT, -keep)

get_likelihood_sigma <- function(row, dist_mat, rho, data){ # helper function for computing likelihood
      # Compute Matérn Covariance Matrix
      mat_cov <- Matern(d = dist_mat, smoothness = row[1], range = rho, phi = 1) + diag(row[2], dim(dist_mat)[1])
      
      # Compute sigma^2
      sigma.squared <- (1/length(data)) * (data %*% chol2inv(chol(mat_cov)) %*% data)[1,1] 
      
      # Compute likelihood
      likelihood <- dmvnorm(data, 
                            mean = rep(0, length(data)), 
                            sigma = sigma.squared * mat_cov,
                            log = TRUE)
      return(likelihood)
}

# distance matrix of years
dist_mat_all <- as.matrix(dist(sort(unique(df$TAX_YEAR) - min(df$TAX_YEAR) + 1), diag=TRUE, upper=TRUE))

set.seed(2727)
orgs_sample <- sample(unique(df$EIN2), size = 50)

combos <- expand.grid(nu = seq(from = 0.01, to = 3, by = 0.07475), 
                      nugget = seq(from = 0, to = 3, by = 0.1))

best_parameters.null <- setNames(data.frame(matrix(ncol = 3, nrow = 0)), c("ID", "nu", "nugget"))
best_parameters.L <- setNames(data.frame(matrix(ncol = 3, nrow = 0)), c("ID", "nu", "nugget"))
best_parameters.R <- setNames(data.frame(matrix(ncol = 3, nrow = 0)), c("ID", "nu", "nugget"))

for (orgID in orgs_sample) {
      # pull their time series
      my_data <- df |> filter(EIN2 == orgID) |>
            mutate(TOT_REV = log1p(TOT_REV),
                   TOT_EXP = log1p(TOT_EXP),
                   TOT_ASSET = log1p(TOT_ASSET))
      all_years <- my_data$TAX_YEAR - min(df$TAX_YEAR) + 1 # all the years we have data for this county
      log_rev <- my_data |> merge(data.frame(TAX_YEAR = 1991:2019), all = TRUE) |> arrange(TAX_YEAR) |> pull(TOT_REV)
      
      candidate <- (my_data  |> filter(topDamage) |> select(TAX_YEAR) |> pull()) - min(df$TAX_YEAR) + 1
      left_years <- all_years[1:which(all_years == candidate)-1]
      right_years <- all_years[which(all_years == candidate):length(all_years)]
      
      ### Null Model ###
      curr_all_years <- c(left_years, right_years)
      centered_rev <- log_rev[curr_all_years] - mean(log_rev[curr_all_years])
      dist_mat <- dist_mat_all[curr_all_years, curr_all_years]
      dist_mat <- (dist_mat - min(dist_mat)) / (max(dist_mat) - min(dist_mat))
      
      # grid search (if doing Nelder-Mead, multiply get_likelihood_sigma by -1)
      likelihood_wrapper.null <- function(pars.vec){
            return(get_likelihood_sigma(row = pars.vec,
                                             dist_mat = dist_mat,
                                             rho = 1,
                                             data = centered_rev))
      }
      
      likelihoods.null <- apply(combos, MARGIN = 1, likelihood_wrapper.null)
      tst <- as.data.frame(list(nu = combos$nu, nugget = combos$nugget, likelihood = likelihoods.null))
      best_parameters.null <- rbind(best_parameters.null, 
                                    as.data.frame(list(ein = orgID,
                                                       nu = tst[which.max(tst$likelihood),]$nu,
                                                       nugget = tst[which.max(tst$likelihood),]$nugget)))
      
      ### Alternative Model ###
      
      # Left
      centered_rev.L <- log_rev[left_years] - mean(log_rev[left_years])
      dist_mat.L <- dist_mat_all[left_years, left_years]
      dist_mat.L <- (dist_mat.L - min(dist_mat.L)) / (max(dist_mat.L) - min(dist_mat.L))
      
      likelihood_wrapper.left <- function(pars.vec){
            return(get_likelihood_sigma(row = pars.vec,
                                             dist_mat = dist_mat.L,
                                             rho = 1,
                                             data = centered_rev.L))
      }
      
      likelihoods.L <- apply(combos, MARGIN = 1, likelihood_wrapper.left)
      tst <- as.data.frame(list(nu = combos$nu, nugget = combos$nugget, likelihood = likelihoods.L))
      best_parameters.L <- rbind(best_parameters.L, 
                                    as.data.frame(list(ein = orgID,
                                                       nu = tst[which.max(tst$likelihood),]$nu,
                                                       nugget = tst[which.max(tst$likelihood),]$nugget)))
      
      # Right
      centered_rev.R <- log_rev[right_years] - mean(log_rev[right_years])
      dist_mat.R <- dist_mat_all[right_years, right_years]
      dist_mat.R <- (dist_mat.R - min(dist_mat.R)) / (max(dist_mat.R) - min(dist_mat.R))
      
      likelihood_wrapper.right <- function(pars.vec){
            return(get_likelihood_sigma(row = pars.vec,
                                             dist_mat = dist_mat.R,
                                             rho = 1,
                                             data = centered_rev.R))
      }
      
      likelihoods.R <- apply(combos, MARGIN = 1, likelihood_wrapper.right)
      tst <- as.data.frame(list(nu = combos$nu, nugget = combos$nugget, likelihood = likelihoods.R))
      best_parameters.R <- rbind(best_parameters.R, 
                                    as.data.frame(list(ein = orgID,
                                                       nu = tst[which.max(tst$likelihood),]$nu,
                                                       nugget = tst[which.max(tst$likelihood),]$nugget)))
}

all_best <- rbind(best_parameters.null, best_parameters.L, best_parameters.R) |> select(nu,nugget)
cl <- kmeans(all_best, 5, iter.max = 20, nstart = 3)
cl$centers

# saveRDS(cl, "gp_data/ORG_init_conds_50.rds")
```

## Nelder-Mead
Note: This took a little over 4 hours to run on my computer (Macbook Pro, Apple M1 Chip, 16 GB). I didn't parallelize it but you could in theory.
```{r}
library(data.table)
library(readr)
library(dplyr)
library(tidyverse)
library(fields)
library(mvtnorm)

df <- readRDS("gp_data/df_eligible_orgs.rds") |> select(-DATA_COUNT, -keep)

get_likelihood_sigma <- function(row, dist_mat, rho, data){ # helper function for computing likelihood
      # Compute Matérn Covariance Matrix
      mat_cov <- Matern(d = dist_mat, smoothness = row[1], range = rho, phi = 1) + diag(row[2], dim(dist_mat)[1])
      
      # Compute sigma^2
      sigma.squared <- (1/length(data)) * (data %*% chol2inv(chol(mat_cov)) %*% data)[1,1] 
      
      # Compute likelihood
      likelihood <- dmvnorm(data, 
                            mean = rep(0, length(data)), 
                            sigma = sigma.squared * mat_cov,
                            log = TRUE)
      return(likelihood)
}

# distance matrix of years
dist_mat_all <- as.matrix(dist(sort(unique(df$TAX_YEAR) - min(df$TAX_YEAR) + 1), diag=TRUE, upper=TRUE))

init_conds <- readRDS("ORG_init_conds_50.rds")$centers

best_parameters.null <- setNames(data.frame(matrix(ncol = 3, nrow = 0)), c("ein", "nu", "nugget"))
best_parameters.L <- setNames(data.frame(matrix(ncol = 3, nrow = 0)), c("ein", "nu", "nugget"))
best_parameters.R <- setNames(data.frame(matrix(ncol = 3, nrow = 0)), c("ein", "nu", "nugget"))

errs <- c()
for (orgID in unique(df$EIN2)) {
      print(orgID)
      # pull their time series
      my_data <- df |> filter(EIN2 == orgID) |>
            mutate(TOT_REV = log1p(TOT_REV),
                   TOT_EXP = log1p(TOT_EXP),
                   TOT_ASSET = log1p(TOT_ASSET))
      all_years <- my_data$TAX_YEAR - min(df$TAX_YEAR) + 1 # all the years we have data for this county
      log_rev <- my_data |> merge(data.frame(TAX_YEAR = 1991:2019), all = TRUE) |> arrange(TAX_YEAR) |> pull(TOT_REV)
      
      candidate <- (my_data  |> filter(topDamage) |> select(TAX_YEAR) |> pull()) - min(df$TAX_YEAR) + 1
      left_years <- all_years[1:which(all_years == candidate)-1]
      right_years <- all_years[which(all_years == candidate):length(all_years)]
      
      ### Null Model ###
      curr_all_years <- c(left_years, right_years)
      centered_rev <- log_rev[curr_all_years] - mean(log_rev[curr_all_years])
      dist_mat <- dist_mat_all[curr_all_years, curr_all_years]
      dist_mat <- (dist_mat - min(dist_mat)) / (max(dist_mat) - min(dist_mat))
      
      likelihood_wrapper.null <- function(pars.vec){
            return(-1 * get_likelihood_sigma(row = pars.vec,
                                             dist_mat = dist_mat,
                                             rho = 1,
                                             data = centered_rev))
      }
      
      tst <- setNames(data.frame(matrix(ncol = 6, nrow = 0)), c("nu.init", "nugg.init", "nu", "nugget", "likelihood", "trial"))
i <- 2      
      for (i in 1:nrow(init_conds)){
            res <- constrOptim(theta = init_conds[i,], 
                               f = likelihood_wrapper.null,
                               grad = NULL,
                               ui = rbind(c(1,0),c(-1,0),c(0,1)), #rbind(c(1,0),c(-1,0),c(0,1))
                               ci = c(0.001,-3.5,0)) #c(0.001,-3.5, 0)
            tst[nrow(tst)+1,] <- c(c(init_conds[i,1], init_conds[i,2], res$par[1], res$par[2], -1*res$value, i))
      }

      best_parameters.null <- rbind(best_parameters.null, 
                                    as.data.frame(list(ein = orgID,
                                                       nu = tst[which.max(tst$likelihood),]$nu,
                                                       nugget = tst[which.max(tst$likelihood),]$nugget)))
      
      ### Alternative Model ###
      
      # Left
      centered_rev.L <- log_rev[left_years] - mean(log_rev[left_years])
      if (var(centered_rev.L) == 0){
            errs <- c(errs, orgID)
            next
            }
      dist_mat.L <- dist_mat_all[left_years, left_years]
      dist_mat.L <- (dist_mat.L - min(dist_mat.L)) / (max(dist_mat.L) - min(dist_mat.L))
      
      likelihood_wrapper.left <- function(pars.vec){
            return(-1 * get_likelihood_sigma(row = pars.vec,
                                             dist_mat = dist_mat.L,
                                             rho = 1,
                                             data = centered_rev.L))
      }
      
      tst <- setNames(data.frame(matrix(ncol = 6, nrow = 0)), c("nu.init", "nugg.init", "nu", "nugget", "likelihood", "trial"))
      for (i in 1:nrow(init_conds)){
            res <- constrOptim(theta = init_conds[i,], 
                               f = likelihood_wrapper.left,
                               grad = NULL,
                               ui = rbind(c(1,0),c(-1,0),c(0,1)), #rbind(c(1,0),c(-1,0),c(0,1))
                               ci = c(0.001,-3.5,0)) #c(0.001,-3.5, 0)
            tst[nrow(tst)+1,] <- c(c(init_conds[i,1], init_conds[i,2], res$par[1], res$par[2], -1*res$value, i))
      }
      best_parameters.L <- rbind(best_parameters.L, 
                                    as.data.frame(list(ein = orgID,
                                                       nu = tst[which.max(tst$likelihood),]$nu,
                                                       nugget = tst[which.max(tst$likelihood),]$nugget)))
      
      # Right
      centered_rev.R <- log_rev[right_years] - mean(log_rev[right_years])
      if (var(centered_rev.R) == 0){
            errs <- c(errs, orgID)
            next
            }
      dist_mat.R <- dist_mat_all[right_years, right_years]
      dist_mat.R <- (dist_mat.R - min(dist_mat.R)) / (max(dist_mat.R) - min(dist_mat.R))
      
      likelihood_wrapper.right <- function(pars.vec){
            return(-1 * get_likelihood_sigma(row = pars.vec,
                                             dist_mat = dist_mat.R,
                                             rho = 1,
                                             data = centered_rev.R))
      }
      
      tst <- setNames(data.frame(matrix(ncol = 6, nrow = 0)), c("nu.init", "nugg.init", "nu", "nugget", "likelihood", "trial"))
      for (i in 1:nrow(init_conds)){
            res <- constrOptim(theta = init_conds[i,], 
                               f = likelihood_wrapper.right,
                               grad = NULL,
                               ui = rbind(c(1,0),c(-1,0),c(0,1)), #rbind(c(1,0),c(-1,0),c(0,1))
                               ci = c(0.001,-3.5,0)) #c(0.001,-3.5, 0)
            tst[nrow(tst)+1,] <- c(c(init_conds[i,1], init_conds[i,2], res$par[1], res$par[2], -1*res$value, i))
      }
      best_parameters.R <- rbind(best_parameters.R, 
                                    as.data.frame(list(ein = orgID,
                                                       nu = tst[which.max(tst$likelihood),]$nu,
                                                       nugget = tst[which.max(tst$likelihood),]$nugget)))

}

# saveRDS(best_parameters.null, "gp_data/ORG_best_null.rds")
# saveRDS(best_parameters.L, "gp_data/ORG_best_L.rds")
# saveRDS(best_parameters.R, "gp_data/ORG_best_R.rds")
```

# LRT
```{r}
library(data.table)
library(readr)
library(dplyr)
library(tidyverse)
library(fields)
library(mvtnorm)

df <- readRDS("gp_data/df_eligible_orgs.rds") |> select(-DATA_COUNT, -keep)

# distance matrix of years
dist_mat_all <- as.matrix(dist(sort(unique(df$TAX_YEAR) - min(df$TAX_YEAR) + 1), diag=TRUE, upper=TRUE))

best_all.null <- readRDS("gp_data/ORG_best_null.rds")
best_all.L <- readRDS("gp_data/ORG_best_L.rds")
best_all.R <- readRDS("gp_data/ORG_best_R.rds")
missing_ein <- union(setdiff(unique(df$EIN2), best_all.L$ein),
                     setdiff(unique(df$EIN2), best_all.R$ein))

# saveRDS(missing_ein, "gp_data/org_missing_ein.rds") # to investigate if needed / to skip in loop below

rho = 1

reject_null <- list()
for (my_org in unique(df$EIN2)) {
      if (my_org %in% missing_ein){next}
      # pull their time series
      my_data <- df |> filter(EIN2 == my_org) |>
            mutate(TOT_REV = log1p(TOT_REV),
                   TOT_EXP = log1p(TOT_EXP),
                   TOT_ASSET = log1p(TOT_ASSET))
      all_years <- my_data$TAX_YEAR - min(df$TAX_YEAR) + 1 # all the years we have data for this county
      log_rev <- my_data |> merge(data.frame(TAX_YEAR = 1991:2019), all = TRUE) |> arrange(TAX_YEAR) |> pull(TOT_REV)
      
      candidate <- (my_data  |> filter(topDamage) |> select(TAX_YEAR) |> pull()) - min(df$TAX_YEAR) + 1
      
      # pull best parameters
      best.null <- best_all.null |> filter(ein == my_org)
      best.L <- best_all.L |> filter(ein == my_org)
      best.R <- best_all.R |> filter(ein == my_org)
      
      
      # Determine the left and right time series corresponding to the current candidate change point
      left_years <- all_years[1:which(all_years == candidate)-1]
      right_years <- all_years[which(all_years == candidate):length(all_years)]
      
      ### Null Hypothesis Model ###
      curr_all_years <- c(left_years, right_years) # Redundant for single candidate
      centered_rev <- log_rev[curr_all_years] - mean(log_rev[curr_all_years]) # center the log revenue values so they are mean 0
      
      dist_mat <- dist_mat_all[curr_all_years, curr_all_years]
      dist_mat <- (dist_mat - min(dist_mat)) / (max(dist_mat) - min(dist_mat))
      Sigma_0 <- Matern(d = dist_mat,
                        smoothness = best.null$nu,
                        range = rho,
                        phi = 1) + diag(best.null$nugget, dim(dist_mat)[1])
      
      sigma.sqrd_0 <- (1/length(centered_rev)) * (centered_rev %*% chol2inv(chol(Sigma_0)) %*% centered_rev)[1,1]
      Sigma_0 <- sigma.sqrd_0 * Sigma_0
      
      ### Alternative Hypothesis Model ###
      # center the log revenue values so they are mean 0
      centered_rev.L <- log_rev[left_years] - mean(log_rev[left_years])
      centered_rev.R <- log_rev[right_years] - mean(log_rev[right_years])
      
      # compute and normalize distance matrices
      dist_mat.L <- dist_mat_all[left_years, left_years]
      dist_mat.L <- (dist_mat.L - min(dist_mat.L)) / (max(dist_mat.L) - min(dist_mat.L))
      
      dist_mat.R <- dist_mat_all[right_years, right_years]
      dist_mat.R <- (dist_mat.R - min(dist_mat.R)) / (max(dist_mat.R) - min(dist_mat.R))
      
      # Compute Matern covariance matrices
      Sigma_L <- Matern(d = dist_mat.L,
                        smoothness = best.L$nu,
                        range = rho,
                        phi = 1) + diag(best.L$nugget, dim(dist_mat.L)[1])
      sigma.sqrd_L <- (1/length(left_years)) * (centered_rev.L %*% chol2inv(chol(Sigma_L)) %*% centered_rev.L)[1,1]
      Sigma_L <- sigma.sqrd_L * Sigma_L
      
      Sigma_R <- Matern(d = dist_mat.R,
                        smoothness = best.R$nu,
                        range = rho,
                        phi = 1) + diag(best.R$nugget, dim(dist_mat.R)[1])
      sigma.sqrd_R <- (1/length(right_years)) * (centered_rev.R %*% chol2inv(chol(Sigma_R)) %*% centered_rev.R)[1,1]
      Sigma_R <- sigma.sqrd_R * Sigma_R
      
      ### Likelihood Ratio Test ###
      L_0 <- dmvnorm(centered_rev, 
                     mean = rep(0, length(centered_rev)), 
                     sigma = Sigma_0,
                     log = TRUE)
      
      L_left <- dmvnorm(centered_rev.L, 
                        mean = rep(0, length(centered_rev.L)), 
                        sigma = Sigma_L,
                        log = TRUE)
      
      L_right <- dmvnorm(centered_rev.R, 
                         mean = rep(0, length(centered_rev.R)), 
                         sigma = Sigma_R,
                         log = TRUE)
      
      L_alt <- L_left + L_right
      
      
      # likelihood ratio test statistic
      lrt <- -2*L_0 + 2*L_alt
      doF <- 4 #  (mu1, mu2, Sigma1, Sigma2, nu1, nu2, nugget1, nugget2) vs (mu, Sigma, nu, nugget) 
      reject_null[my_org] <- (lrt > qchisq(p = 0.05, df = doF, lower.tail = FALSE))
}

sum(unlist(reject_null)) / length(reject_null) # 37.25 % of the time we have enough evidence to reject the null
```



# Empirical Distribution Org-Level
## Picking 50 random candidate change points per org
```{r}
library(readr)
library(dplyr)
library(tidyverse)

set.seed(2727)
df <- readRDS("gp_data/df_eligible_orgs.rds") |> select(-DATA_COUNT, -keep)

# When picking random candidate change points to create the empirical distribution, still need to ensure that there is a "buffer" of data around each candidate
df <- df |> filter(!(geoid_2010 %in% readRDS("gp_data/org_missing_ein.rds"))) |> 
      group_by(EIN2) |>
      mutate(n = n(),
             row_num = row_number(),
             eligible = (row_num > 5 & row_num <= n-4)) |> ungroup()

candidates_all <- list()
for (i in 1:50) {
      candidates <- df |> group_by(EIN2) |>
            filter(eligible) |> # only randomly pick from eligible points
            slice_sample(n = 1) |>
            select(EIN2, TAX_YEAR)
      
      candidates_list <- candidates |> pull(TAX_YEAR) |> as.list()
      names(candidates_list) <- candidates |> pull(EIN2)
      
      candidates_all[[as.character(i)]] <- candidates_list
}
# saveRDS(candidates_all, "gp_data/ORG_random_candidates50.rds")
```

## Hyperparameter Optimization
### Round 1: Grid Search
```{r}
library(data.table)
library(readr)
library(dplyr)
library(tidyverse)
library(fields)
library(mvtnorm)

df <- readRDS("gp_data/df_eligible_orgs.rds") |> select(-DATA_COUNT, -keep)
candidates_all <- readRDS("gp_data/ORG_random_candidates50.rds")

get_likelihood_sigma <- function(row, dist_mat, rho, data){ # helper function for computing likelihood
      # Compute Matérn Covariance Matrix
      mat_cov <- Matern(d = dist_mat, smoothness = row[1], range = rho, phi = 1) + diag(row[2], dim(dist_mat)[1])
      
      # Compute sigma^2
      sigma.squared <- (1/length(data)) * (data %*% chol2inv(chol(mat_cov)) %*% data)[1,1] 
      
      # Compute likelihood
      likelihood <- dmvnorm(data, 
                            mean = rep(0, length(data)), 
                            sigma = sigma.squared * mat_cov,
                            log = TRUE)
      return(likelihood)
}


# distance matrix of years
dist_mat_all <- as.matrix(dist(sort(unique(df$TAX_YEAR) - min(df$TAX_YEAR) + 1), diag=TRUE, upper=TRUE))

set.seed(2727)
orgs_sample <- sample(unique(df$EIN2), size = 50)

combos <- expand.grid(nu = seq(from = 0.01, to = 3, by = 0.07475), 
                      nugget = seq(from = 0, to = 3, by = 0.1))

best_parameters.null <- setNames(data.frame(matrix(ncol = 4, nrow = 0)), c("ein", "nu", "nugget", "trial"))
best_parameters.L <- setNames(data.frame(matrix(ncol = 4, nrow = 0)), c("ein", "nu", "nugget", "trial"))
best_parameters.R <- setNames(data.frame(matrix(ncol = 4, nrow = 0)), c("ein", "nu", "nugget", "trial"))

for (orgID in orgs_sample) {
      # pull their time series
      my_data <- df |> filter(EIN2 == orgID) |>
            mutate(TOT_REV = log1p(TOT_REV),
                   TOT_EXP = log1p(TOT_EXP),
                   TOT_ASSET = log1p(TOT_ASSET))
      all_years <- my_data$TAX_YEAR - min(df$TAX_YEAR) + 1 # all the years we have data for this county
      log_rev <- my_data |> merge(data.frame(TAX_YEAR = 1991:2019), all = TRUE) |> arrange(TAX_YEAR) |> pull(TOT_REV)
      
      for (i in names(candidates_all)){      
            candidate <- candidates_all[[i]][[orgID]] - min(df$TAX_YEAR) + 1
            left_years <- all_years[1:which(all_years == candidate)-1]
            right_years <- all_years[which(all_years == candidate):length(all_years)]
            
            ### Null Model ###
            curr_all_years <- c(left_years, right_years)
            centered_rev <- log_rev[curr_all_years] - mean(log_rev[curr_all_years])
            dist_mat <- dist_mat_all[curr_all_years, curr_all_years]
            dist_mat <- (dist_mat - min(dist_mat)) / (max(dist_mat) - min(dist_mat))
            
            # grid search (if doing Nelder-Mead, multiply get_likelihood_sigma by -1)
            likelihood_wrapper.null <- function(pars.vec){
                  return(get_likelihood_sigma(row = pars.vec,
                                                   dist_mat = dist_mat,
                                                   rho = 1,
                                                   data = centered_rev))
            }
            
            likelihoods.null <- apply(combos, MARGIN = 1, likelihood_wrapper.null)
            tst <- as.data.frame(list(nu = combos$nu, nugget = combos$nugget, likelihood = likelihoods.null))
            best_parameters.null <- rbind(best_parameters.null, 
                                          as.data.frame(list(ein = orgID,
                                                             nu = tst[which.max(tst$likelihood),]$nu,
                                                             nugget = tst[which.max(tst$likelihood),]$nugget,
                                                             trial = i)))
            
            ### Alternative Model ###
            
            # Left
            centered_rev.L <- log_rev[left_years] - mean(log_rev[left_years])
            dist_mat.L <- dist_mat_all[left_years, left_years]
            dist_mat.L <- (dist_mat.L - min(dist_mat.L)) / (max(dist_mat.L) - min(dist_mat.L))
            
            likelihood_wrapper.left <- function(pars.vec){
                  return(get_likelihood_sigma(row = pars.vec,
                                                   dist_mat = dist_mat.L,
                                                   rho = 1,
                                                   data = centered_rev.L))
            }
            
            likelihoods.L <- apply(combos, MARGIN = 1, likelihood_wrapper.left)
            tst <- as.data.frame(list(nu = combos$nu, nugget = combos$nugget, likelihood = likelihoods.L))
            best_parameters.L <- rbind(best_parameters.L, 
                                          as.data.frame(list(ein = orgID,
                                                             nu = tst[which.max(tst$likelihood),]$nu,
                                                             nugget = tst[which.max(tst$likelihood),]$nugget,
                                                             trial = i)))
            
            # Right
            centered_rev.R <- log_rev[right_years] - mean(log_rev[right_years])
            dist_mat.R <- dist_mat_all[right_years, right_years]
            dist_mat.R <- (dist_mat.R - min(dist_mat.R)) / (max(dist_mat.R) - min(dist_mat.R))
            
            likelihood_wrapper.right <- function(pars.vec){
                  return(get_likelihood_sigma(row = pars.vec,
                                                   dist_mat = dist_mat.R,
                                                   rho = 1,
                                                   data = centered_rev.R))
            }
            
            likelihoods.R <- apply(combos, MARGIN = 1, likelihood_wrapper.right)
            tst <- as.data.frame(list(nu = combos$nu, nugget = combos$nugget, likelihood = likelihoods.R))
            best_parameters.R <- rbind(best_parameters.R, 
                                          as.data.frame(list(ein = orgID,
                                                             nu = tst[which.max(tst$likelihood),]$nu,
                                                             nugget = tst[which.max(tst$likelihood),]$nugget,
                                                             trial = i)))
            }
}

all_best <- rbind(best_parameters.null, best_parameters.L, best_parameters.R) |> select(nu,nugget)
cl <- kmeans(all_best, 5, iter.max = 20, nstart = 3)
cl$centers

# saveRDS(cl, "gp_data/ORG_empirical_init_conds_50.rds")
```

### Round 2: Gradient Descent with multiple starts
This part is in a separate R file called "org_empirical_opt.R" due to wanting the ability to run in parallel in the background. Before proceeding to the next section, run org_empirical_opt.R.

## LRT
```{r}
library(readr)
library(dplyr)
library(tidyverse)

glued <- rbind(readRDS("gp_data/ORG_empirical_best_1.rds"), 
               readRDS("gp_data/ORG_empirical_best_2.rds"),
               readRDS("gp_data/ORG_empirical_best_3.rds"),
               readRDS("gp_data/ORG_empirical_best_4.rds"),
               readRDS("gp_data/ORG_empirical_best_5.rds"))

# Creating a list of lists
best_all <- glued |> 
      mutate(ID = paste0(ein,".",trial)) |> 
      select(-ein,-trial) # First, creating an ID for each org,trial pair
best_all <- split(best_all, best_all$ID) # The outer list names are these IDs
best_all <- lapply(best_all, function(x) {split(x,x$type)}) # The inner list names are null, left, right with elements being the values nu and nugget
# Example: best_all$ID$left$nu

saveRDS(best_all, "gp_data/ORG_best_empirical_all.rds")
```

LRTs
```{r}
library(readr)
library(dplyr)
library(tidyverse)
library(fields)
library(mvtnorm)
library(doParallel)

candidates_all <- readRDS("gp_data/ORG_random_candidates50.rds")
df <- readRDS("gp_data/df_eligible_orgs.rds") |> select(-DATA_COUNT, -keep)

# distance matrix of years
dist_mat_all <- as.matrix(dist(sort(unique(df$TAX_YEAR) - min(df$TAX_YEAR) + 1), diag=TRUE, upper=TRUE))

best_all <- readRDS("gp_data/ORG_best_empirical_all.rds")

rho = 1

# note: .inorder = FALSE so the outer list won't be in trial order... I think for our purposes ok
res <- foreach(trialID = 1:3, .packages = c("dplyr", "fields", "mvtnorm"), .inorder = FALSE) %dopar% { # length(candidates_all)
      reject_null <- list()
      print(paste0("Trial: ", trialID))
      for (orgID in unique(df$EIN2)){
            ID <- paste0(orgID, ".", trialID)
            if (!(ID %in% names(best_all))){
                  print(paste("Missing ID:", ID))
                  next
            }
            # pull their time series
            my_data <- df |> filter(EIN2 == orgID) |>
                  mutate(TOT_REV = log1p(TOT_REV),
                         TOT_EXP = log1p(TOT_EXP),
                         TOT_ASSET = log1p(TOT_ASSET))
            all_years <- my_data$TAX_YEAR - min(df$TAX_YEAR) + 1 # all the years we have data for this county
            log_rev <- my_data |> merge(data.frame(TAX_YEAR = 1991:2019), all = TRUE) |> arrange(TAX_YEAR) |> pull(TOT_REV)
            
            candidate <- candidates_all[[trialID]][[orgID]] - min(df$TAX_YEAR) + 1
            
            # pull best parameters
            best.curr <- best_all[[ID]] # best.curr$left$nu
      
            # Determine the left and right time series corresponding to the current candidate change point
            left_years <- all_years[1:which(all_years == candidate)-1]
            right_years <- all_years[which(all_years == candidate):length(all_years)]
            
            ### Null Hypothesis Model ###
            curr_all_years <- c(left_years, right_years) # Redundant for single candidate
            centered_rev <- log_rev[curr_all_years] - mean(log_rev[curr_all_years]) # center the log revenue values so they are mean 0
            
            dist_mat <- dist_mat_all[curr_all_years, curr_all_years]
            dist_mat <- (dist_mat - min(dist_mat)) / (max(dist_mat) - min(dist_mat))
            Sigma_0 <- Matern(d = dist_mat,
                              smoothness = best.curr$null$nu,
                              range = rho,
                              phi = 1) + diag(best.curr$null$nugget, dim(dist_mat)[1])
            
            sigma.sqrd_0 <- (1/length(centered_rev)) * (centered_rev %*% chol2inv(chol(Sigma_0)) %*% centered_rev)[1,1]
            Sigma_0 <- sigma.sqrd_0 * Sigma_0
            
            ### Alternative Hypothesis Model ###
            # center the log revenue values so they are mean 0
            centered_rev.L <- log_rev[left_years] - mean(log_rev[left_years])
            centered_rev.R <- log_rev[right_years] - mean(log_rev[right_years])
            
            # compute and normalize distance matrices
            dist_mat.L <- dist_mat_all[left_years, left_years]
            dist_mat.L <- (dist_mat.L - min(dist_mat.L)) / (max(dist_mat.L) - min(dist_mat.L))
            
            dist_mat.R <- dist_mat_all[right_years, right_years]
            dist_mat.R <- (dist_mat.R - min(dist_mat.R)) / (max(dist_mat.R) - min(dist_mat.R))
            
            # Compute Matern covariance matrices
            Sigma_L <- Matern(d = dist_mat.L,
                        smoothness = best.curr$left$nu,
                        range = rho,
                        phi = 1) + diag(best.curr$left$nugget, dim(dist_mat.L)[1])
            sigma.sqrd_L <- (1/length(left_years)) * (centered_rev.L %*% chol2inv(chol(Sigma_L)) %*% centered_rev.L)[1,1]
            Sigma_L <- sigma.sqrd_L * Sigma_L
            
            Sigma_R <- Matern(d = dist_mat.R,
                        smoothness = best.curr$right$nu,
                        range = rho,
                        phi = 1) + diag(best.curr$right$nugget, dim(dist_mat.R)[1])
            sigma.sqrd_R <- (1/length(right_years)) * (centered_rev.R %*% chol2inv(chol(Sigma_R)) %*% centered_rev.R)[1,1]
            Sigma_R <- sigma.sqrd_R * Sigma_R
            
            ### Likelihood Ratio Test ###
            L_0 <- dmvnorm(centered_rev, 
                           mean = rep(0, length(centered_rev)), 
                           sigma = Sigma_0,
                           log = TRUE)
            
            L_left <- dmvnorm(centered_rev.L, 
                              mean = rep(0, length(centered_rev.L)), 
                              sigma = Sigma_L,
                              log = TRUE)
            
            L_right <- dmvnorm(centered_rev.R, 
                               mean = rep(0, length(centered_rev.R)), 
                               sigma = Sigma_R,
                               log = TRUE)
            
            L_alt <- L_left + L_right
      
            
            # likelihood ratio test statistic
            lrt <- -2*L_0 + 2*L_alt
            doF <- 4 #  (mu1, mu2, Sigma1, Sigma2, nu1, nu2, nugget1, nugget2) vs (mu, Sigma, nu, nugget)
            reject_null[[orgID]] <- (lrt > qchisq(p = 0.05, df = doF, lower.tail = FALSE))

      }
      # reject_null_all[[as.character(trialID)]] <- reject_null
      reject_null
}

res.final <- unlist(lapply(res, function(x){sum(unlist(x)) / length(x)}))
hist(res.final)
sd(res.final)
```

Bootstrapping
```{r}
library(readr)
library(dplyr)
library(tidyverse)
library(doParallel)

res <- readRDS("org_empirical_lrt_res.rds")
res <- unlist(res)
res <- split(res, names(res))
res <- lapply (res, unname)

empirical <- foreach(i = 1:1000, .inorder = FALSE) %do% {
      tst <- lapply(res, function(x){sample(x, 1)})
      sum(unlist(tst)) / length(tst)
}

hist(unlist(empirical), col = "#fe6100", 
     main = "Organization-Level Empirical Distribution", 
     xlab = "Proportion of times the null is rejected")
quantile(unlist(empirical), probs = c(0.025, 0.5, 0.975)) # middle 95% of data is between 37.27% and 38.45%
mean(unlist(empirical))
```
